koda: Deep Learning-Enhanced Pipeline for Keyword Detection in Document Images

### 2020-01-10 paper/paper.tex
Add conclusions to paper

%TODO FORMULA

@@

TODO: talk about the iterator and put an image with bounding boxes

@@

TODO

>>>>

\begin{equation*}
	\begin{bmatrix} \cos(\sigma_1) & \sin(\sigma_1) \\ \cos(\sigma_2) & \sin(\sigma_2) \end{bmatrix}
	\begin{bmatrix} x \\ y \end{bmatrix}
	=
	\begin{bmatrix} \gamma_1 \\ \gamma_2 \end{bmatrix}
\end{equation*}
\begin{equation*}
	Ax = b
\end{equation*}

@@

Due to the keyword highlighting feature, it was crucial to get the position of single words rather than blocks of text. This is easily achieved using Tesseract's \textit{Iterators}, by setting the \textit{Page Iterator Level} to \texttt{WORD}. Thereafter, KODA can cycle through each word, filtering out the ones with low confidence and extracting the bounding boxes, as well as the text, as shown in Fig. \ref{fig:ocr}.

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1\textwidth]{ocr.png}}
	\caption{Example of OCR word segmenting}
	\label{fig:ocr}
\end{figure}

@@

The proposed pipeline is able to correctly recognize and analyze the majority of document pictures in real-world scenarios, searching for the given keywords and preserving the original perspective, as shown in Fig. \ref{fig:result}.

\begin{figure}[H]
	\makebox[\textwidth][c]{\includegraphics[width=1\textwidth]{result.png}}
	\caption{Example of KODA pipeline result for keyword "the". Overall output image on the left and close up on the right.}
	\label{fig:result}
\end{figure}

That said, KODA is still limited in certain situations. Firstly, the edge detection model was trained specifically to recognize white documents and, as a result, struggles with colored ones.
Moreover, although the deep learning-based edge detection offers superior results compared to traditional techniques, it is computationally expensive. In particular, the model itself weights about 360 megabytes and takes about 0.5/1 seconds to process the image on a modern desktop CPU, which makes it unsuitable for mobile applications.

Future improvements may focus on the creation of a less computationally and memory expensive edge detection, so that the pipeline can be ported on a mobile device.
